realData

### 2022-05-25 analyses/complexSim.Rmd
cleaned, licensed version of cbnn

---
title: "iterSim"
output: html_document
params:
  epo: 2
  patience: 1
  iteration: 2
  layer1: 50
  layer2: 50
  layer3: 25
  layer4: 25
  drpt: 0.5
---

@@

easysim<-F
hardsim<-T
numSamp<-2000
```

```{r easySimpletests,eval=easysim}
start_time <- Sys.time()

BrierIPAList<-list()
cScore<-list()

pos<-1
for(iter in 1:iteration){

  #############################
  ###Data generation
  #############################

  cov<-data.frame(id=1:numSamp,
                  z1=c(rep(1,numSamp/2),rep(0,numSamp/2)),
                  z2=c(rnorm(numSamp/2,10,0.5),rnorm(numSamp/2,0,0.5)),
                  z3=c(rnorm(numSamp/2,-3,0.5),rnorm(numSamp/2,8,0.5))
  )

  dat <- simsurv(dist = "exponential",
                 lambdas =.05,
                 betas = c(z1 = .5,z2=.5,z3=.5),
                 x = cov,
                 tdefunction = "log",
                 maxt = 1
  )
  colnames(dat)<-c("id","time","status")
  samp<-sample(seq(1,nrow(dat),by=1), floor(nrow(dat)*(0.1))) #random censoring
  dat$status[samp]<-0
  # Merge the simulated event times onto covariate data frame
  data <- merge(cov, dat)
  covs<-colnames(data)

  ##########################
  ###Split data
  ##########################
  samp<-sample(seq(1,nrow(data),by=1), floor(nrow(data)*.8))
  data<-data[,-1]
  data[,-c(1,5)]<-as.data.frame(sapply(data[,-c(1,5)], function(x) (x - min(x, na.rm = T)) / (max(x, na.rm = T) - min(x, na.rm=T))))
  train<-data[samp,]
  test<-data[-samp,-c(ncol(data))]
  fullTest<-data[-samp,,drop=F]
  times<-seq(from=0,
             to=max(test$time),
             length.out = 200
  )
  times<-times[-c(1,length(times))]

  ##########################
  ###DSM
  ##########################
  source_python('src/dsmScript.py')
  dsmSurv<-dsmfitter(train=train,fullTest=fullTest,bsize=bsize,epochs=epo,tPos=ncol(train)-2,ePos=ncol(train)-1)
  if((sum(is.na(dsmSurv))==ncol(dsmSurv)*nrow(dsmSurv))){

    dsmSurv<-dsmfitter(train=train,fullTest=fullTest,bsize=bsize,epochs=epo)
    py_run_string("del dsmfitter")
    rm(dsmfitter)
    iteration<-iteration+1
    next
  }
  colnames(dsmSurv) <-seq(0.01,1,by=0.01)
  dsmSurvProper<-pyProcess(dsmSurv,times=times)
  colnames(dsmSurvProper) <-seq(0,1,length.out = ncol(dsmSurvProper))
  py_run_string("del dsmfitter")
  rm(dsmfitter)

  ##########################
  ###casebase optimal model
  ##########################
  final_mod_cb_glm <- fitSmoothHazard(status~z1+z2+z3,#z1:z2:z3+z1+z2+z3,+z1:z3+z1:z2:z3
                                      data = train,
                                      time = "time",
                                      event="status",
                                      ratio = 100
  )

  summary(final_mod_cb_glm)
  tglmAbsRisk<-absoluteRisk(final_mod_cb_glm,time=times,newdata=test,type="CI")
  tglmAbsRisk<-as.data.frame(tglmAbsRisk)
  rownames(tglmAbsRisk)<-tglmAbsRisk$time
  trueGlmProper<- t(tglmAbsRisk[-1,-1])

  class(trueGlmProper)<-c("tunnel",class(trueGlmProper))

  ##########################
  ###casebase + splines
  ##########################
  mod_cb_glm <- fitSmoothHazard(status~bs(time)+.-time,
                                data = train,
                                time = "time",
                                event="status",
                                ratio = 100
  )
  glmAbsRisk<-absoluteRisk(mod_cb_glm,time=times,newdata=test,type="CI")
  glmAbsRisk<-as.data.frame(glmAbsRisk)
  rownames(glmAbsRisk)<-glmAbsRisk$time
  glmProper<- t(glmAbsRisk[-1,-1])
  class(glmProper)<-c("tunnel",class(glmProper))

  ############################
  ###DeepSurv
  ############################  
  coxnn<-deepsurv(Surv(time, status) ~ .,data = train, frac = 0.2, activation = "relu",
                  num_nodes = c(layer1,layer2,layer3,layer4), dropout = drpt,
                  early_stopping = TRUE, epochs = epo,
                  batch_size = bsize,device = "cpu",best_weights=T,
                  patience = patience,min_delta=min_delta,batch_norm = F,
                  learning_rate = 0.001,lr_decay=10^-7)

  coxnnsurv<- predict(coxnn,newdata = test,type="survival")
  colnames(coxnnsurv)<-seq(0,1,length.out = ncol(coxnnsurv))
  cnnCleaned<-pyProcess(coxnnsurv,times=times)
  colnames(cnnCleaned)<-seq(0,1,length.out = ncol(cnnCleaned))
  ############################
  ###Deephit
  ############################  
  source_python('src/deephitter.py')
  hitnnSurv=fitDeephit(train,fullTest,bsize,epo,patience=patience,min_delta=min_delta,drpt=drpt)
  hitnnSurv<-t(hitnnSurv)
  colnames(hitnnSurv)<-seq(0,1,length.out = ncol(hitnnSurv))
  deephitCleaned<-pyProcess(hitnnSurv,times=times)
  colnames(deephitCleaned)<-seq(0,1,length.out = ncol(deephitCleaned))
  py_run_string("del fitDeephit")
  rm(fitDeephit)

  ############################
  ###PMNNsplines
  ############################  
  covars_input<-layer_input(shape=c(length(colnames(mod_cb_glm$data))-2+3),
                            name = 'main_input'
  )
  covars_output<-covars_input%>% 
    layer_dense(units=layer1,use_bias = T,activation = 'relu')%>%
    layer_dropout(drpt)%>%
    layer_dense(units=layer2,use_bias = T,activation = 'relu')%>%
    layer_dropout(drpt)%>%
    layer_dense(units=layer3,use_bias = T,activation = 'relu')%>%
    layer_dropout(drpt)%>%
    layer_dense(units=layer4,use_bias = T,activation = 'relu')%>%
    layer_dropout(drpt)%>%
    layer_dense(units=1,use_bias = T)

  rownames(annPreds)<-annPreds[,1]
  annProperpoly<- t(annPreds[,-1])

  class(annProperpoly)<-c("tunnel",class(annProperpoly)) 
  brierFinalResults <- Score(list("Cox_Lin" = cox,
                                  'CB_Logi'=glmProper,
                                  'DeepSurv'=cnnCleaned,
                                  'DeepHit'=deephitCleaned,
                                  'PMNN_Spline'=annProper,
                                  'Optimal'=trueGlmProper,
                                  'PMNN_Poly'=annProperpoly,
                                  'dsm'=dsmSurvProper) ,#'dsm'=dsmCleaned,
                                  data =fullTest, 
                             formula = Hist(time, status != 0) ~ 1, summary = c("risks","IPA","ibs"), 
                             se.fit = FALSE, metrics = "brier", contrasts = FALSE, times = times)
  BrierIPAList[[pos]]<-brierFinalResults$Brier$score
  ########################
  ###C-Index
  ########################
  tempTims<-   as.numeric(colnames(annProper))
  tempTims<-head(tempTims, -15)
  tempTims<-tail(tempTims, -10)
  cScoreTemp<-matrix(NA,nrow=length(tempTims),ncol=9)
  et_train<-as.matrix(train)#[,c(5,4)]
  et_test<-as.matrix(fullTest[,c(5,4)])
  colnames(cScoreTemp)<-c('times', "Cox_Lin",'CB_Logi','DeepSurv','DeepHit',
                          'PMNN_Spline','Optimal','PMNN_Poly','dsm')
  cScoreTemp[,1]<- tempTims

  a<-survfit(cox, newdata=fullTest,times=times)
  rownames(a$surv)<-a$time
  coxlinSurv<-pyProcess(t(a$surv),times=times)
  colnames(coxlinSurv)<-seq(0,1,length.out = ncol(coxlinSurv))

  riskList<-list(coxlinSurv,
                 glmProper,
                 cnnCleaned,
                 deephitCleaned,
                 annProper,
                 annProperpoly
  )

  cScore[[pos]]<-cIndexSummary(et_train=et_train
                               , et_test=et_test,
                               riskList=riskList,
                               cScore=cScoreTemp
  )

  saveRDS(BrierIPAList,'100easyBrier.rds')
  saveRDS(cScore,'100easycidx.rds')
  pos<-pos+1
}

end_time <- Sys.time()

@@

start_time <- Sys.time()
BrierIPAList<-list()
cScore<-list()
pos<-1
for(iter in 1:iteration){

@@

  #########################
  ###Simulate data
  #########################
  samp<-sample(seq(1,nrow(data),by=1), floor(nrow(data)*.8))
  data<-data[,-1]
  data[,-c(1,5)]<-as.data.frame(sapply(data[,-c(1,5)], function(x) (x - min(x, na.rm = T)) / (max(x, na.rm = T) - min(x, na.rm=T))))
  train<-data[samp,]
  test<-data[-samp,-c(ncol(data))]
  fullTest<-data[-samp,,drop=F]
  times<-seq(from=0,
             to=max(test$time),
             length.out = 200
  )
  times<-times[-c(1,length(times))]

@@

  ######################
  ###C-Index
  ######################
  tempTims<-   as.numeric(colnames(annProper))
  tempTims<-head(tempTims, -15)
  tempTims<-tail(tempTims, -10)
  cScoreTemp<-matrix(NA,nrow=length(tempTims),ncol=8)
  et_train<-as.matrix(train)#[,c(5,4)]
  et_test<-as.matrix(fullTest[,c(5,4)])
  colnames(cScoreTemp)<-c('times', "Cox_Lin",'CB_Logi','DeepSurv','DeepHit',
                          'PMNN_Spline','Optimal','PMNN_Poly')#,'dsm')
  cScoreTemp[,1]<- tempTims
  a<-survfit(cox, newdata=fullTest,times=times)
  rownames(a$surv)<-a$time
  coxlinSurv<-pyProcess(t(a$surv),times=times)
  colnames(coxlinSurv)<-seq(0,1,length.out = ncol(coxlinSurv))
  riskList<-list(coxlinSurv,
                 glmProper,
                 cnnCleaned,
                 deephitCleaned,
                 annProper,
                 annProperpoly
  )

  cScore[[pos]]<-cIndexSummary(et_train=et_train
                               , et_test=et_test,
                               riskList=riskList,
                               cScore=cScoreTemp
  )

>>>>

---
title: "iterSim"
output: html_document
params:
  epo: 2000
  patience: 10
  iteration: 2
  layer1: 50
  layer2: 50
  layer3: 25
  layer4: 25
  drpt: 0.5
---

@@

hardsim<-T
numSamp<-2000
```

@@

start_time <- Sys.time()
BrierIPAList<-list()
cScore<-list()
pos<-1

while (pos <= iteration) {

@@

  #########################
  ###Simulate data
  #########################
  samp<-sample(seq(1,nrow(data),by=1), floor(nrow(data)*.8))
  data<-data[,-1]
  data[,-c(1,5)]<-as.data.frame(sapply(data[,-c(1,5)], function(x) (x - min(x, na.rm = T)) / (max(x, na.rm = T) - min(x, na.rm=T))))
  train<-data[samp,]
  test<-data[-samp,-c(ncol(data))]
  fullTest<-data[-samp,,drop=F]
  times<-seq(from=min(test$time),
             to=max(test$time),
             length.out = 200
  )
  times<-times[-c(1,length(times))]

@@

  #######################
  ###Cox 
  ######################
  a<-survfit(cox, newdata=fullTest,times=times)
  rownames(a$surv)<-a$time
  coxlinSurv<-pyProcess(t(a$surv),times=times)
  colnames(coxlinSurv)<-seq(0,1,length.out = ncol(coxlinSurv))

  ######################
  ###C-Index
  ######################

  riskList<-list(coxlinSurv,
                 glmProper,
                 cnnCleaned,
                 deephitCleaned,
                 annProper,
                 trueGlmProper,
                 annProperpoly
  )

  tempTims<-   as.numeric(colnames(annProper))
  tempTims<-head(tempTims, -1)
  tempTims<-tail(tempTims, -1)
  cScoreTemp<-matrix(NA,nrow=length(tempTims),ncol=length(riskList)+1)
  et_train<-as.matrix(train)[,c(5,4)]
  et_test<-as.matrix(fullTest[,c(5,4)])
  colnames(cScoreTemp)<-c('times', "Cox_Lin",'CB_Logi','DeepSurv','DeepHit',
                          'PMNN_Spline','Optimal','PMNN_Poly')#,'dsm')
  cScoreTemp[,1]<- tempTims

  cScore[[pos]]<-cIndexSummary(et_train=et_train,
                               et_test=et_test,
                               riskList=riskList,
                               cScore=cScoreTemp
  )

### 2022-05-25 analyses/proofOfConceptWeights.Rmd
cleaned, licensed version of cbnn

epo=2
bsize=512
min_delta = 10^-7
patience = 1
iteration=5

eval_support<-T
source_python('src/getSUP.py')

########################
###sharedHyperparams
########################

@@

```{r modelsSUPPORT,eval=eval_support}

start_time <- Sys.time()
BrierIPAList<-list()
cScore<-list()

data<- as.data.frame(do.call(cbind, getSupportPycox()))
colnames(data)[ncol(data)-1]<-'time'
colnames(data)[ncol(data)]<-'status'
data<-as.data.frame(model.matrix(~.,data)[,-1])
data<-as.data.frame(sapply(data, function(x) (x - min(x, na.rm = T)) / (max(x, na.rm = T) - min(x, na.rm=T))))

covs<-colnames(data)

#split training/testing
samp<-sample(seq(1,nrow(data),by=1), floor(nrow(data)*.80)) 
trainOG<-data[samp,]
test<-data[-samp,-c(ncol(data))]
fullTest<-data[-samp,,drop=F]

pos=1
for(iter in 1:iteration){

  samp<-sample(seq(1,nrow(trainOG),by=1) , nrow(trainOG),replace = T) 
  train<-trainOG[samp,]

  times<-seq(from=0,
             to=max(test$time),
             length.out = 200
  )
  times<-times[-c(1,length(times))]

  ######################
  ###casebase + splines
  ######################
  mod_cb_glm <- fitSmoothHazard(status~bs(time)+.-time,
                                data = train,
                                time = "time",
                                event="status",
                                ratio = 100
  )

  glmAbsRisk<-as.data.frame(absoluteRisk(mod_cb_glm,time=times,newdata=test,type="CI"))
  rownames(glmAbsRisk)<-glmAbsRisk$time
  #prepare to run through riskRegression
  glmProper<- t(glmAbsRisk[-1,-1])
  class(glmProper)<-c("tunnel",class(glmProper))

  ######################
  ###DeepSurv
  ######################
  coxnn<-deepsurv(Surv(time, status) ~ .,data = train, frac = 0.2, activation = "relu",
                  num_nodes = c(layer1,layer2,layer3,layer4,), dropout = drpt,
                  early_stopping = TRUE, epochs = epo,
                  batch_size = bsize,device = "cpu",best_weights=T,
                  patience = patience,min_delta=min_delta,batch_norm = F,
                  learning_rate = 0.001,lr_decay=10^-7)
  coxnnsurv<- predict(coxnn,newdata = test,type="survival")
  colnames(coxnnsurv)<-seq(0,1,length.out = ncol(coxnnsurv))
  cnnCleaned<-pyProcess(coxnnsurv,times=times)
  colnames(cnnCleaned)<-seq(0,1,length.out = ncol(cnnCleaned))

  ######################
  ###Deephit
  ######################
  source_python('deephitter.py')
  hitnnSurv=fitDeephit(train,fullTest,bsize,epo)
  hitnnSurv<-t(hitnnSurv)
  colnames(hitnnSurv)<-seq(0,1,length.out = ncol(hitnnSurv))
  deephitCleaned<-pyProcess(hitnnSurv,times=times)
  colnames(deephitCleaned)<-seq(0,1,length.out = ncol(deephitCleaned))
  py_run_string("del fitDeephit")
  rm(fitDeephit)

  ######################
  ###PMNN splines
  ######################
  covars_input<-layer_input(shape=c(length(colnames(mod_cb_glm$data))-2+3),
                            name = 'main_input'
  )
  covars_output<-covars_input%>% #layer_batch_normalization()%>%
    layer_dense(units=layer1,use_bias = T,activation = 'relu')%>%
    layer_dropout(drpt)%>%
    layer_dense(units=layer2,use_bias = T,activation = 'relu')%>%
    layer_dropout(drpt)%>%
    layer_dense(units=layer3,use_bias = T,activation = 'relu')%>%
    layer_dropout(drpt)%>%
    layer_dense(units=layer4,use_bias = T,activation = 'relu')%>%
    layer_dropout(drpt)%>%
    layer_dense(units=1,use_bias = T)

  pmnn<-pmnnModel(features=colnames(mod_cb_glm$data)[-ncol(mod_cb_glm$data)],
                  feature_input = covars_input,
                  feature_output = covars_output,
                  originalData = mod_cb_glm$data,
                  offset=mod_cb_glm$offset,
                  timeVar = "time",
                  eventVar= "status"
  )

  fit<-fitSmoothHazSpline(pmnn,epochs=epo,batch_size = bsize,verbose=0)
  annPreds<-aarSplines(fit,
                       times=times,
                       x_test=test
  )
  rownames(annPreds)<-annPreds[,1]
  annProper<- t(annPreds[,-1])
  class(annProper)<-c("tunnel",class(annProper))

  ######################
  ###coxph
  ######################
  cox<-coxph(Surv(time, status) ~ ., data = train,x=T)

  ######################
  ###PMNN
  ######################
  covars_input<-layer_input(shape=c(length(colnames(mod_cb_glm$data))-2),
                            name = 'main_input')

  covars_output<-covars_input%>% #layer_batch_normalization()%>%
    layer_dense(units=layer1,use_bias = T,activation = 'relu')%>%
    layer_dropout(drpt)%>%
    layer_dense(units=layer2,use_bias = T,activation = 'relu')%>%
    layer_dropout(drpt)%>%
    layer_dense(units=layer3,use_bias = T,activation = 'relu')%>%
    layer_dropout(drpt)%>%
    layer_dense(units=layer4,use_bias = T,activation = 'relu')%>%
    layer_dropout(drpt)%>%
    layer_dense(units=1,use_bias = T)

  pmnn<-pmnnModel(features=colnames(mod_cb_glm$data)[-ncol(mod_cb_glm$data)],
                  feature_input = covars_input,
                  feature_output = covars_output,
                  originalData = mod_cb_glm$data,
                  offset=mod_cb_glm$offset,
                  timeVar = "time",
                  eventVar= "status"
  )

  fit<-fitSmoothHaz(pmnn,epochs=epo,batch_size = bsize,verbose=0)
  annPreds<-aar(fit,
                times=times,
                x_test=test
  )

  rownames(annPreds)<-annPreds[,1]
  annProperpoly<- t(annPreds[,-1])
  class(annProperpoly)<-c("tunnel",class(annProperpoly))

  ######################
  ###IPA calculation
  ######################
  brierFinalResults <- Score(list("Cox_Lin" = cox,'CB_Logi'=glmProper,
                                  'DeepSurv'=cnnCleaned,'DeepHit'=deephitCleaned,
                                  'PMNN_Spline'=annProper,'PMNN_Poly'=annProperpoly),
                             data =fullTest, 
                             formula = Hist(time, status != 0) ~ 1, summary = c("risks","IPA","ibs"), 
                             se.fit = FALSE, metrics = "brier", contrasts = FALSE, times = times)
  BrierIPAList[[pos]]<-brierFinalResults$Brier$score

  ######################
  ###C-Index
  ######################
  tempTims<-as.numeric(colnames(annProper))
  tempTims<-head(tempTims, -15)
  tempTims<-tail(tempTims, -10)
  cScoreTemp<-matrix(NA,nrow=length(tempTims),ncol=7)

  et_train<-as.matrix(train)
  et_test<-as.matrix(fullTest[,c(11,10)])
  colnames(cScoreTemp)<-c('times', "Cox_Lin",'CB_Logi','DeepSurv','DeepHit',
                          'PMNN_Spline','PMNN_Poly')
  cScoreTemp[,1]<- tempTims

  ### Cox is not calculated, so abrisk is calculated here.
  a<-survfit(cox, newdata=fullTest,times=times)
  rownames(a$surv)<-a$time
  coxlinSurv<-pyProcess(t(a$surv),times=times)
  colnames(coxlinSurv)<-seq(0,1,length.out = ncol(coxlinSurv))
  riskList<-list(coxlinSurv,
                 glmProper,
                 cnnCleaned,
                 deephitCleaned,
                 annProper,
                 annProperpoly
  )

  cScore[[pos]]<-cIndexSummary(et_train=et_train
                               , et_test=et_test,
                               riskList=riskList,
                               cScore=cScoreTemp
  )
  pos=pos+1
  saveRDS(BrierIPAList,'100supBrier.rds')
  saveRDS(cScore,'100supcidx.rds')

}

ggplot(data=brierFinalResults$Brier$score, aes(x=times,y=Brier,col=model))+
  geom_line()
ggplot(data=brierFinalResults$Brier$score, aes(x=times,y=IPA,col=model))+
  geom_line()

end_time <- Sys.time()

end_time-start_time

```{r modelsMETABRIC,eval=eval_metabric}

start_time <- Sys.time()

#pycox<-reticulate::import("pycox")
#numpy<-reticulate::import("numpy")
#a<-pycox$datasets$metabric$read_df
#b<-numpy$asarray(a)

############################
###Data clean and prep
############################
metabric<-getMetabric()
colnames(metabric)[ncol(metabric)-1]<-'time'
colnames(metabric)[ncol(metabric)]<-'status'
data<-as.data.frame(model.matrix(~.,metabric)[,-1])
data<-as.data.frame(sapply(data, function(x) (x - min(x, na.rm = T)) / (max(x, na.rm = T) - min(x, na.rm=T))))
covs<-colnames(data)

samp<-sample(seq(1,nrow(data),by=1), floor(nrow(data)*.80)) 
trainOG<-data[samp,]
test<-data[-samp,-c(ncol(data))]

fullTest<-data[-samp,,drop=F]

############################
###Prep Loop
############################
BrierIPAList<-list()
cScore<-list()
pos=1

for(iter in 1:iteration){

  ############################
  ###Bootstrap samples
  ############################  
  samp<-sample(seq(1,nrow(trainOG),by=1) , nrow(trainOG),replace = T) 
  train<-trainOG[samp,]

  times<-seq(from=0,
             to=max(test$time),
             length.out = 200
  )
  times<-times[-c(1,length(times))]
  times<-unique(times)

  ############################
  ###DSM
  ############################  
  source_python('dsmScript.py')
  dsmSurv<-dsmfitter(train=train,fullTest=fullTest,bsize=bsize,epochs=epo,tPos=ncol(train)-2,ePos=ncol(train)-1)
  #sometimes, dsm fails to converge so we keep trying until it succeeds
  if((sum(is.na(dsmSurv))==ncol(dsmSurv)*nrow(dsmSurv))){
    dsmSurv<-dsmfitter(train=train,fullTest=fullTest,bsize=bsize,epochs=epo,tPos=ncol(train)-2,ePos=ncol(train)-1)
    py_run_string("del dsmfitter")
    rm(dsmfitter)
    iteration<-iteration+1
    next
  }
  colnames(dsmSurv) <-seq(0.01,1,by=0.01)
  dsmSurvProper<-pyProcess(dsmSurv,times=times)
  colnames(dsmSurvProper) <-seq(0,1,length.out = ncol(dsmSurvProper))
  py_run_string("del dsmfitter")
  rm(dsmfitter)

  ############################
  ###casebase + splines
  ############################  
  mod_cb_glm <- fitSmoothHazard(status~bs(time)+.-time,
                                data = train,
                                time = "time",
                                event="status",
                                ratio = 100
  )

  glmAbsRisk<-absoluteRisk(mod_cb_glm,time=times,newdata=test,type="CI")
  glmAbsRisk<-as.data.frame(glmAbsRisk)
  rownames(glmAbsRisk)<-glmAbsRisk$time
  glmProper<- t(glmAbsRisk[-1,-1])
  class(glmProper)<-c("tunnel",class(glmProper))

  ############################
  ###DeepSurv
  ############################  
  coxnn<-deepsurv(Surv(time, status) ~ .,data = train, frac = 0.2, activation = "relu",
                  num_nodes = c(layer1,layer2,layer3,layer4), dropout = drpt,
                  early_stopping = TRUE, epochs = epo,
                  batch_size = bsize,device = "cpu",best_weights=T,
                  patience = patience,min_delta=min_delta,batch_norm = F,
                  learning_rate = 0.001,lr_decay=10^-7)

  coxnnsurv<- predict(coxnn,newdata = test,type="survival")
  colnames(coxnnsurv)<-seq(0,1,length.out = ncol(coxnnsurv))
  cnnCleaned<-pyProcess(coxnnsurv,times=times)
  colnames(cnnCleaned)<-seq(0,1,length.out = ncol(cnnCleaned))
  ############################
  ###Deephit
  ############################  
  source_python('deephitter.py')
  hitnnSurv=fitDeephit(train,fullTest,bsize,10)
  hitnnSurv<-t(hitnnSurv)
  colnames(hitnnSurv)<-seq(0,1,length.out = ncol(hitnnSurv))
  deephitCleaned<-pyProcess(hitnnSurv,times=times)
  colnames(deephitCleaned)<-seq(0,1,length.out = ncol(deephitCleaned))
  py_run_string("del fitDeephit")
  rm(fitDeephit)

  ############################
  ###PMNNsplines
  ############################  
  covars_input<-layer_input(shape=c(length(colnames(mod_cb_glm$data))-2+3),
                            name = 'main_input'
  )
  covars_output<-covars_input%>% 
    layer_dense(units=layer1,use_bias = T,activation = 'relu')%>%
    layer_dropout(drpt)%>%
    layer_dense(units=layer2,use_bias = T,activation = 'relu')%>%
    layer_dropout(drpt)%>%
    layer_dense(units=layer3,use_bias = T,activation = 'relu')%>%
    layer_dropout(drpt)%>%
    layer_dense(units=layer4,use_bias = T,activation = 'relu')%>%
    layer_dropout(drpt)%>%
    layer_dense(units=1,use_bias = T)

  pmnn<-pmnnModel(features=colnames(mod_cb_glm$data)[-ncol(mod_cb_glm$data)],
                  feature_input = covars_input,
                  feature_output = covars_output,
                  originalData = mod_cb_glm$data,
                  offset=mod_cb_glm$offset,
                  timeVar = "time",
                  eventVar= "status"
  )

  fit<-fitSmoothHazSpline(pmnn,epochs=epo,batch_size = bsize,verbose=0)
  annPreds<-aarSplines(fit,
                       times=times,
                       x_test=test
  )

  rownames(annPreds)<-annPreds[,1]
  annProper<- t(annPreds[,-1])
  class(annProper)<-c("tunnel",class(annProper))

  ############################
  ###coxph
  ############################  
  cox<-coxph(Surv(time, status) ~ ., data = train,x=T)

  ############################
  ###PMNN
  ############################  
  covars_input<-layer_input(shape=c(length(colnames(mod_cb_glm$data))-2),
                            name = 'main_input')

  covars_output<-covars_input%>% #layer_batch_normalization()%>%
    layer_dense(units=layer1,use_bias = T,activation = 'relu')%>%
    layer_dropout(drpt)%>%
    layer_dense(units=layer2,use_bias = T,activation = 'relu')%>%
    layer_dropout(drpt)%>%
    layer_dense(units=layer3,use_bias = T,activation = 'relu')%>%
    layer_dropout(drpt)%>%
    layer_dense(units=layer4,use_bias = T,activation = 'relu')%>%
    layer_dropout(drpt)%>%
    layer_dense(units=1,use_bias = T)

  pmnn<-pmnnModel(features=colnames(mod_cb_glm$data)[-ncol(mod_cb_glm$data)],
                  feature_input = covars_input,
                  feature_output = covars_output,
                  originalData = mod_cb_glm$data,
                  offset=mod_cb_glm$offset,
                  timeVar = "time",
                  eventVar= "status"
  )
  fit<-fitSmoothHaz(pmnn,epochs=epo,batch_size = bsize,verbose=0)
  annPreds<-aar(fit,
                times=times,
                x_test=test
  )
  rownames(annPreds)<-annPreds[,1]
  annProperpoly<- t(annPreds[,-1])
  class(annProperpoly)<-c("tunnel",class(annProperpoly)) 
  ############################
  ###Brier Score
  ############################  
  brierFinalResults <- Score(list("Cox_Lin" = cox,'CB_Logi'=glmProper,
                                  'DeepSurv'=cnnCleaned,'DeepHit'=deephitCleaned,
                                  'PMNN_Spline'=annProper,'PMNN_Poly'=annProperpoly,
                                  'dsm'=dsmSurvProper),
                             data =fullTest, 
                             formula = Hist(time, status != 0) ~ 1, summary = c("risks","IPA","ibs"), 
                             se.fit = FALSE, metrics = "brier", contrasts = FALSE, times = times)
  BrierIPAList[[pos]]<-brierFinalResults$Brier$score

  ############################
  ###C-Index
  ############################  
  tempTims<-   as.numeric(colnames(annProper))
  tempTims<-head(tempTims, -15)
  tempTims<-tail(tempTims, -10)
  cScoreTemp<-matrix(NA,nrow=length(tempTims),ncol=8)
  et_train<-as.matrix(train)
  et_test<-as.matrix(fullTest[,c(11,10)])
  colnames(cScoreTemp)<-c('times', "Cox_Lin",'CB_Logi','DeepSurv','DeepHit',
                          'PMNN_Spline','PMNN_Poly','dsm')

  cScoreTemp[,1]<- tempTims

  a<-survfit(cox, newdata=fullTest,times=times)
  rownames(a$surv)<-a$time
  coxlinSurv<-pyProcess(t(a$surv),times=times)
  colnames(coxlinSurv)<-seq(0,1,length.out = ncol(coxlinSurv))
  riskList<-list(coxlinSurv,
                 glmProper,
                 cnnCleaned,
                 deephitCleaned,
                 annProper,
                 annProperpoly
  )

  cScore[[pos]]<-cIndexSummary(et_train=et_train
                               , et_test=et_test,
                               riskList=riskList,
                               cScore=cScoreTemp
  )
  saveRDS(BrierIPAList,'100MetaBrier.rds')
  saveRDS(cScore,'100Metacidx.rds')
  pos=pos+1

} 
end_time <- Sys.time()

end_time-start_time

ggplot(data=brierFinalResults$Brier$score, aes(x=times,y=Brier,col=model))+
  geom_line()
ggplot(data=brierFinalResults$Brier$score, aes(x=times,y=IPA,col=model))+
  geom_line()

```{r ERSPCproofofconcept,eval=F}

data<-ERSPC
colnames(data)<-c("ScrArm","time","status")

mod_cb_glm <- fitSmoothHazard(status~.,
                              data =data,
                              time = "time",
                              event="status",
                              ratio = 100
)

@@

pmnn<-pmnnModel(features=colnames(mod_cb_glm$data)[-ncol(mod_cb_glm$data)],
                feature_input = covars_input,
                feature_output = covars_output,
                originalData = mod_cb_glm$data,
                offset=mod_cb_glm$offset,
                timeVar = "time",
                eventVar= "status",
                optimizer= 'rmsprop'
)

fit<-fitSmoothHaz(pmnn,epochs=12000,#15000
                  batch_size = 159893,#159893,#
                  verbose=0,monitor = "loss",val_split=0)
times<-seq(0,max(data$time),by=0.01)
get_weights(fit$model)
coef(mod_cb_glm)
annPreds<-aar(fit,
              times=times,
              x_test=data[1,]
)
#absoluteRisk(mod_cb_glm,time=times,newdata=data[1,],type="CI")

@@

saveRDS(results,"../paper/figures/proofOfConceptWeights.rds")

>>>>

epo=2
bsize=512
min_delta = 10^-7
patience = 1
iteration=5
########################
###sharedHyperparams
########################

@@

```{r ERSPCproofofconcept,eval=T}
##originally used 1 sample ,now using all data
data<-ERSPC
colnames(data)<-c("ScrArm","time","status")
  data<-as.data.frame(model.matrix(~.,data)[,-1])
mod_cb_glm <- fitSmoothHazard(status~.,
                              data =data,
                              time = "time",
                              event="status",
                              ratio = 100
)

@@

pmnn<-pmnnModel(features=colnames(mod_cb_glm$data)[-ncol(mod_cb_glm$data)],
                feature_input = covars_input,
                feature_output = covars_output,
                originalData = mod_cb_glm$data,
                offset=mod_cb_glm$offset,
                timeVar = "time",
                eventVar= "status",
                optimizer= 'adam'
)

fit<-fitSmoothHaz(pmnn,epochs=12000,#15000
                  batch_size = 1024,#159893,#
                  verbose=0,monitor = "loss",val_split=0)
times<-seq(0,max(data$time),length.out=100)
get_weights(fit$model)
coef(mod_cb_glm)

startOG <- Sys.time()
annPreds<-aarOld(fit,
              times=times,
              x_test=data[1:100,]
)
endOG <- Sys.time()
startq <- Sys.time()
annQuick<-aar(fit,times=times,x_test=data[1:100,])
endq <- Sys.time()

startOG-endOG
startq-endq

@@

#saveRDS(results,"../paper/figures/proofOfConceptWeights.rds")
